PANCHANGE_analysis

### 2020-08-20 PANCHANGE_analysis.Rmd
added plots and tables for phq gad and ocir

```{r Gender per Sample chisquare}
dat %>% 
  specify(Gender ~ Sample)  %>% 
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "Chisq") %>% 
  visualize()# +
#  geom_vline(aes(xintercept = observed_stat), color = "red") # add a vertical line for the data
```

# highest_education
```{r highest_education per Sample}
dat %>%
  group_by(highest_education, Sample) %>%
  count(highest_education)
```

# Key worker status
```{r Key worker status per sample}
dat %>%
  group_by(key_worker, Sample) %>%
  count(key_worker)
```

# COVID
## COVID swab test positive
```{r COVID positive swap}
dat %>%
  group_by(respiratory.throat_swab_test_nose, Sample) %>%
  count(respiratory.throat_swab_test_nose)
```

## antibody test
```{r COVID positive antibody test}
dat %>%
  group_by(respiratory.results_antibody_test, Sample) %>%
  count(respiratory.results_antibody_test)
```

## COVID probable diagnosis
```{r COVID probable diagnosis}
dat %>%
  group_by(covid_probable_case_incl_screening, Sample) %>%
  count(covid_probable_case_incl_screening)
```

@@

## gad
```{r gad gather to long format Time_points}
dat.long.gad.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "gad.diff_score",
    all_of(gad.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Time_point_raw,
    gad.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "gad.diff_score_", "")) %>%
  select(-Time_point_raw)

@@

# phq

```{r phq gather to long format Time_points}
dat.long.phq.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "phq.diff_score",
    all_of(phq.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Time_point_raw,
    phq.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "phq.diff_score_", "")) %>%
  select(-Time_point_raw) %>%
  drop_na(phq.diff_score)

@@

```{r}
dat.long.phq.diff %>%
  filter(Time_point != "prepan_retro") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
   geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
    ) +
  theme_minimal()
```

```{r}
dat.long.phq.diff %>%
  filter(Time_point == "prepan_retro") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
   geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
    ) +
  theme_minimal()
```

```{r gather to long format Time_points}
dat.long.ocir.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "ocir.diff_score",
    all_of(ocir.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Time_point_raw,
    ocir.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "ocir.diff_score_", "")) %>%
  select(-Time_point_raw)

@@

```{r}
dat.long.ocir.diff %>%
  ggplot(mapping = aes(y = ocir.diff_score)) +
  geom_bar() +
  theme_minimal() +
  facet_wrap(facets = vars(Time_point))
```

>>>>

# highest_education
```{r highest_education per Sample}
dat %>%
  count(highest_education, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))
```

# Key worker status
```{r Key worker status per sample}
dat %>%
  count(key_worker, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))
```

# COVID
## COVID swab test positive
```{r COVID positive swap}
dat %>%
  count(respiratory.throat_swab_test_nose, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))
```

## antibody test
```{r COVID positive antibody test}
dat %>%
  count(respiratory.results_antibody_test, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))
```

## COVID probable diagnosis
```{r COVID probable diagnosis}
dat %>%
  count(covid_probable_case_incl_screening, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))
```

@@

## gad

```{r descriptives gad.diff_score_cols}
gad.numeric_table <- dat %>% 
#  group_by(dem.sex) %>%
  summarise_at( 
    vars(
      "Base - prepan" = gad.diff_score_base_prepan,
      "Base - retro" = gad.diff_score_base_retro,
      "Prepan - retro" = gad.diff_score_prepan_retro,
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

gad.numeric_table
```

```{r smart numeric summary tables}
# reshape the table
gad.numeric_summary_table_reshaped <- gad.numeric_table %>% 
  gather(key, value) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
    ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

gad.numeric_summary_table_reshaped
```

Table for knitting
gad diff summary table
```{r gad diff summary table}
kable(gad.numeric_summary_table_reshaped)
```

```{r gad gather to long format Time_points}
dat.long.gad.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "gad.diff_score",
    all_of(gad.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Time_point_raw,
    gad.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "gad.diff_score_", "")) %>%
  select(-Time_point_raw)

@@

## phq

```{r descriptives phq.diff_score_cols}
phq.numeric_table <- dat %>% 
  #  group_by(dem.sex) %>%
  summarise_at( 
    vars(
      "Base - prepan" = phq.diff_score_base_prepan,
      "Base - retro" = phq.diff_score_base_retro,
      "Prepan - retro" = phq.diff_score_prepan_retro,
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

phq.numeric_table
```

```{r smart numeric summary tables}
# reshape the table
phq.numeric_summary_table_reshaped <- phq.numeric_table %>% 
  gather(key, value) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

phq.numeric_summary_table_reshaped
```

Table for knitting
phq diff summary table
```{r phq diff summary table}
kable(phq.numeric_summary_table_reshaped)
```

```{r phq gather to long format Time_points}
dat.long.phq.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "phq.diff_score",
    all_of(phq.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Time_point_raw,
    phq.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "phq.diff_score_", "")) %>%
  select(-Time_point_raw)

@@

makes this into percentages
```{r phq absolut plot}
dat.long.phq.diff %>%
  ggplot(mapping = aes(y = phq.diff_score)) +
  geom_bar() +
  theme_minimal() +
  facet_wrap(facets = vars(Time_point))
```

```{r phq percentage plot prepan_retro}
dat.long.phq.diff %>%
  filter(Time_point != "prepan_retro") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference phq7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
```

```{r phq plot prepan_retro diff}
dat.long.phq.diff %>%
  filter(Time_point == "prepan_retro") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference phq7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nPrepandemic vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Retrospective"))
```

## ocir

```{r descriptives ocir.diff_score_cols}
ocir.numeric_table <- dat %>% 
  #  group_by(dem.sex) %>%
  summarise_at( 
    vars(
      "Base - prepan" = ocir.diff_score_base_prepan,
      "Base - retro" = ocir.diff_score_base_retro,
      "Prepan - retro" = ocir.diff_score_prepan_retro,
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

ocir.numeric_table
```

```{r smart numeric summary tables}
# reshape the table
ocir.numeric_summary_table_reshaped <- ocir.numeric_table %>% 
  gather(key, value) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

ocir.numeric_summary_table_reshaped
```

Table for knitting
ocir diff summary table
```{r ocir diff summary table}
kable(ocir.numeric_summary_table_reshaped)
```

```{r ocir gather to long format Time_points}
dat.long.ocir.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "ocir.diff_score",
    all_of(ocir.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Time_point_raw,
    ocir.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "ocir.diff_score_", "")) %>%
  select(-Time_point_raw)

@@

makes this into percentages
```{r ocir absolut plot}
dat.long.ocir.diff %>%
  ggplot(mapping = aes(y = ocir.diff_score)) +
  geom_bar() +
  theme_minimal() +
  facet_wrap(facets = vars(Time_point))
```

```{r ocir percentage plot prepan_retro}
dat.long.ocir.diff %>%
  filter(Time_point != "prepan_retro") %>%
  ggplot(mapping = aes(
    x = ocir.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference ocir7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
```

```{r ocir plot prepan_retro diff}
dat.long.ocir.diff %>%
  filter(Time_point == "prepan_retro") %>%
  ggplot(mapping = aes(
    x = ocir.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference ocir7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nPrepandemic vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Retrospective"))
```

+++ Everything underneath here is only SCRATCH
